---
title: "BabyWeightSmoking"
author: "Ray Chen"
date: "2025-05-28"
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Data
```{r}
data <- read.csv("BabyWeightSmoking.csv")
head(data)
```

## Boxplot of MotherSmoke and BirthWeight
```{r}
boxplot_smoke <- boxplot(BirthWeight ~ MotherSmoke, data = data)
```

## Two Sample t-test
null hypothesis: There is no difference in population mean age of mothers who smoke and those who do not smoke
```{r}
t_test_smoking <- t.test(MothersAge ~ MotherSmoke, data = data)
t_test_smoking
```
Since p value is significantly large, we fail to reject the null hypothesis

## Scatter graph of MothersAge versus BirthWeight and linear regression model for prediction
```{r}
plot(data$MothersAge, data$BirthWeight, 
     xlab = "Mother's Age", 
     ylab = "Birth Weight", 
     main = "Scatter Plot of Mother's Age and Birth Weight",)
abline(lm(BirthWeight ~ MothersAge, data = data))

```

## Prediction of BirthWeight given MothersAge 40 years old using linear regression
```{r}
model <- lm(BirthWeight ~ MothersAge, data = data)
predict(model, data.frame(MothersAge = 40))
```
